EDIpack: A generic and interoperable Lanczos-based solver for quantum impurity problems

### 2025-05-26 06_conclusions_acknowledgement_appendix.tex
Updates from Overleaf

% TODO: include funding information
\paragraph{Funding information}
L.C. acknowledge support from Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) thr\-ough the cluster of excellence ``CUI: Advanced Imaging of Matter" of the Deutsche Forschungsgemeinschaft (DFG EXC 2056, Project ID 390715994). Ratefully acknowledges the scientific support and HPC resources provided by the Erlangen National High Performance Computing Center (NHR@FAU) of the Friedrich-Alexander-Universität Erlangen-Nürnberg (FAU) under the NHR project b158cb. NHR funding is provided by federal and Bavarian state authorities. NHR@FAU hardware is partially funded by the German Research Foundation (DFG)– 440719683.
I.K. acknowledge support from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (Grant agreement No.~854843-FASTCORR).
%S.G.
%G.B
%A.K.
%F.P
%M.W.
%G.M.
%L.dM.
%G.S.
%M.C.
%A.A.

@@

{\tt Monicelli} is an esoteric programming language based on the LLVM
toolchain.
It is written in C++ and offers wrappers for the basic
types and operations thereof. The syntax replicates a cultural italian
phenomenon known as ``supercazzola", a rambling nonsensical discourse
which gives the false impression of carrying an actual meaning,
introduced in the trilogy movies ``Amici Miei'', directed by Mario
Monicelli (see
\href{https://it.wikipedia.org/wiki/Amici_miei}{it.wikipedia.org/wiki/Amici\_miei}).

The {\tt Monicelli} language can be found at
\href{https://github.com/esseks/monicelli.git}{github.com/esseks/monicelli.git}
and can be installed using CMake. The software depends on C++
compiler with {\tt stdlib}, LLVM and in some cases {\tt libz} library. The installation gives access to the {\tt
  Monicelli} compiler {\tt mcc}, which statically links LLVM. 
We believe the discourse flow of this language is best captured by 
illustrating its features via a paraphrase of the original supercazzola, an epic dialogue between a traffic policeman (V), count Mascetti (M) and G. Perozzi (P) (see
\href{https://it.wikipedia.org/wiki/Supercazzola#Origine}{it.wikipedia.org/wiki/Supercazzola}
and \href{https://www.youtube.com/watch?v=SF8YUFdP6eU}{Movie Scene}).

\noindent
V: {\it Lei ha clacsonato?}\\
P: {\it Tu ha clacsonato?}\\
M: {\it Tarapia tapioco, prematurata l'interfaccia, o scherziamo?}\\
V: {\it Prego}?\\
M: {\it Scusi noi siamo in Monicelli, come fosse un linguaggio esoterico
basato su C++ e utilizzante la toolchain di LLVM anche per Linux e
Unix soltanto in due, oppure in quattro anche scribai con il file
sorgente {\tt hm\_bethe.mc}?  Come {\tt
  github.com/lcrippa/prematurata\_la\_dmft}, per esempio?}\\
V: {\it Ma che DMFT, mi faccia il piacere! Questi signori stavano
programmano loro, non si intrometta!}\\
M: {\it Ma no, dico, mi porga il file {\tt bagaglio.cpp}. Le vede le
funzioni? Lo vede che interfacciano gli array, non supportati da
Monicelli, e prematurano anche! 
Ora io le direi, anche con il rispetto per l'autorità, anche solo le
due parole come install {\tt Monicelli} from
\href{github.com/esseks/monicelli.git}{https://github.com/esseks/monicelli.git}
e compila il file {\tt hm\_bethe.mc}, per esempio.}\\
V: {\it Basta così! Mi seguano nel programma di test!}\\
P: {\it No, no, no, attenzione! Il loop dmft completo \`e supportato
secondo la Ref.~\onlinecite{Georges1996RMP}, abbia pazienza,
senn\`o.... Plotta i dati, anche un pochino di Green's function e
Self-energy in prefettura.}\\
M: {\it Senza contare che {\tt prematurata\_la\_dmft} ha perso i contatti con il tarapia tapioco, dopo.}\\
V: {\it Ho bello che capito. Si farà finta di passar da bischeri!}\\

@@

\begin{lstlisting}[style=cstyle]
bituma le funzioni ausiliarie che vengono dal bagaglio
...
blinda la supercazzola leggi o scherziamo?
blinda la supercazzola iniziailsolver o scherziamo?
blinda la supercazzola risolvi o scherziamo?
blinda la supercazzola prendilasigma o scherziamo?
blinda la supercazzola prendilbagno con l`elemento Necchi, il valore Sassaroli o scherziamo?
...
\end{lstlisting}

@@

\paragraph{Usage}.
The source code can be retrieved from
\href{https://github.com/lcrippa/prematurata_la_dmft}{github.com/lcrippa/prematurata\_la\_dmft}. 
The {\tt src} directory contains several files, including the source
code {\tt hm\_bethe.mc} implementing the DMFT algorithm, an auxiliary file {\tt bagaglio.cpp} which
contains a number of functions implementing complex algebra, array
costruction and interfacing the \NAME procedures. The directory also
contains an example of input file and a converged bath parametrization
for the Bethe lattice solution at $U=2$.

>>>>

% TODO: include funding information
\paragraph{Funding information}
L.C. acknowledge support from Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) thr\-ough the cluster of excellence ``CUI: Advanced Imaging of Matter" of the Deutsche Forschungsgemeinschaft (DFG EXC 2056, Project ID 390715994). Ratefully acknowledges the scientific support and HPC resources provided by the Erlangen National High Performance Computing Center (NHR@FAU) of the Friedrich-Alexander-Universität Erlangen-Nürnberg (FAU) under the NHR project b158cb. NHR funding is provided by federal and Bavarian state authorities. NHR@FAU hardware is partially funded by the German Research Foundation (DFG)– 440719683.
I.K. acknowledges support from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (Grant agreement No.~854843-FASTCORR).
G.S. and A.K. acknowledge financial support by the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) through FOR 5249 (project-id 449872909, Project P05), and the W\"urzburg-Dresden Cluster of Excellence on Complexity and Topology in Quantum Matter-ct.qmat (EXC 2147, project-id 390858490).
%S.G.
%G.B
%A.K.
%F.P
%M.W.
%G.M.
%L.dM.
%G.S.
%M.C.
%A.A.

@@

{\tt Monicelli} is an esoteric programming language based on the LLVM
toolchain.
It is written in C++ and offers wrappers for the basic
types and operations thereof. The syntax replicates a cultural italian
phenomenon known as ``supercazzola", a rambling nonsensical discourse
which gives the false impression of carrying an actual meaning,
introduced in the movies trilogy ``Amici Miei'', directed by Mario
Monicelli (see
\href{https://it.wikipedia.org/wiki/Amici_miei}{it.wikipedia.org/wiki/Amici\_miei}).

The {\tt Monicelli} language can be found at
\href{https://github.com/esseks/monicelli.git}{github.com/esseks/monicelli.git}
and can be installed using CMake. The software depends on C++
compiler with {\tt stdlib}, LLVM and in some cases {\tt libz} library. The installation gives access to the {\tt
  Monicelli} compiler {\tt mcc}, which statically links LLVM. 
We believe the discourse flow of this language is best captured by 
illustrating its features and \NAME interface via a paraphrase of the original supercazzola, an epic dialogue between a traffic policeman (V), count Mascetti (M) and G. Perozzi (P) (see
\href{https://it.wikipedia.org/wiki/Supercazzola#Origine}{it.wikipedia.org/wiki/Supercazzola}
and \href{https://www.youtube.com/watch?v=SF8YUFdP6eU}{Movie Scene}).

\noindent
V: {\it Lei ha clacsonato?}\\
P: {\it Tu ha clacsonato?}\\
M: {\it Tarapia tapioco, prematurata l'interfaccia, o scherziamo?}\\
V: {\it Prego}?\\
M: {\it Scusi noi siamo in Monicelli, come fosse un linguaggio esoterico
basato su C++ e utilizzante la toolchain di LLVM anche per Linux e
Unix soltanto in due, oppure in quattro anche scribai con il file
sorgente {\tt hm\_bethe.mc}?  Come {\tt
  github.com/lcrippa/prematurata\_la\_dmft}, per esempio?}\\
V: {\it Ma che DMFT, mi faccia il piacere! Questi signori stavano
programmano loro, non si intrometta!}\\
M: {\it Ma no, dico, mi porga il file {\tt bagaglio.cpp}. Le vede le
funzioni? Lo vede che interfacciano gli array, non supportati da
Monicelli, e prematurano anche! 
Ora io le direi, anche con il rispetto per l'autorità, anche solo le
due parole come install {\tt Monicelli} from
\url{https://github.com/esseks/monicelli.git}
e compila il file {\tt hm\_bethe.mc}, per esempio.}\\
V: {\it Basta così! Mi seguano nel programma di test!}\\
P: {\it No, no, no, attenzione! Il loop dmft completo \`e supportato
secondo la Ref.~\onlinecite{Georges1996RMP}, abbia pazienza,
senn\`o.... Plotta i dati, anche un pochino di Green's function e
Self-energy in prefettura.}\\
M: {\it Senza contare che {\tt prematurata\_la\_dmft} ha perso i contatti con il tarapia tapioco, dopo.}\\
V: {\it Ho bello che capito. Si farà finta di passar da bischeri!}\\

@@

\lstset{breaklines=true, breakindent=1em}
\begin{lstlisting}[style=cstyle]
bituma le funzioni ausiliarie che vengono dal bagaglio
...
blinda la supercazzola leggi o scherziamo?
blinda la supercazzola iniziailsolver o scherziamo?
blinda la supercazzola risolvi o scherziamo?
blinda la supercazzola prendilasigma o scherziamo?
blinda la supercazzola prendilbagno con l`elemento Necchi, il valore Sassaroli o scherziamo?
...
\end{lstlisting}

@@

\paragraph{Usage.}
The source code can be retrieved from
\href{https://github.com/lcrippa/prematurata_la_dmft}{github.com/lcrippa/prematurata\_la\_dmft}. 
The {\tt src} directory contains several files, including the source
code {\tt hm\_bethe.mc} implementing the DMFT algorithm, an auxiliary file {\tt bagaglio.cpp} which
contains a number of functions implementing complex algebra, array
costruction and interfacing the \NAME procedures. The directory also
contains an example of input file and a converged bath parametrization
for the Bethe lattice solution at $U=2$.
